\section{Recommendation}

\subsection{Practises}
The future could include interplanetary colonization, as space is a limited resource if we are confined to the earth.
Colonizing other planets would no longer limit humans by the finite spacial resource of earth.
Another practice could be more types of leisurely activities, such as arts, gaming, sports and other entertainment.
With the possibility of machine-assisted labor, machine-assisted white-collar work could also be practiced with highly advanced AI and machine learning, which would consequently make most things humans do optional.

\subsection{Expanded demographic}
The future could also include the following group:

\begin{itemize}
    \item The poor.
    \item The disabled.
    \item The less educated.
    \item People who wish to do physically labor-intensive tasks.
\end{itemize}

\subsection{Assumptions}
Given the assumption of renewable green sources of energy production, I would not change this assumption.
The alternative would not be sustainable, and therefore have consequences in the future.

\subsection{Summary}
The 15th of August 2461 in New Huygens on Mars, a day like any other. It is 20 degrees Celcius with low to modest wind and statistically average humidity. 
Immediately upon waking up, the curtains unfold to let the sun illuminate the surroundings. 
Jeeves-3000 the ultimate butler robot will like always assist with the morning routine that includes a health checkup and undesirable symptom relief.
The day is new and should not start on a bad note, which is exactly why Gordon-Botsay the ultimate cook robot, has been preparing exactly the right breakfast for satisfying personal tastebuds in addition to excellent nourishment. 
The only obligations that await for the day, are those that are self-imposed. 
Challenges, experiences, learning opportunities, technological progress, research or anything else that someone might fancy is freely available to all regardless of any attribute like gender, birth origin or race.
Although the 15th of august is a day like most others, it is by no means a mundane day. 
It is however the day that an eSport tournament in the new full-dive virtual reality game Gun Art Online will be held.
It is also a day of great discovery, as a long-standing "thought-to-be" impossible physical theory of instant communication has for the first time been proved. 
With instant communication, it enables the technology to communicate instantaneously with earth and all other colonies throughout the human empire.  
Instant communication, yet another power-hungry technology is soon to be realized, but there is no need for concern.
The advent of miniature black hole reactors provides all the energy that humans would probably ever need.
With the vast technological advancement of Microsoft computer systems, AI has solved all of humanity's problems. 
Humans live with and preserve a biodiverse ecosystem, and have built a solid foundation for preserving the balance of the universe with an impressive affinity for sustainability.
With all amenities provided through highly advanced technologies, everyone has full agency over their lives and what they wish to spend their time with, whether it be recreational, socializing, working or anything else.

